Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-05-28 hid2-urban-building-cicd.tex
final version before submission

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images
\usepackage[T1]{fontenc}
\usepackage{subcaption}
\usepackage{url}
\usepackage{xcolor}
\definecolor{darkred}{rgb}{0.6, 0, 0}
\definecolor{darkgreen}{rgb}{0, 0.5, 0}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,      % Enable colored links
    linkcolor=darkred,    % Color for internal links
    filecolor=darkgreen,  % Color for file links
    urlcolor=darkblue,    % Color for external URLs
    citecolor=darkmagenta % Color for citations
}

\begin{document}
\title{Enhancing Urban Building Simulations in HiDALGO2 through CI/CD Innovations}
\author{Vincent Chabannes \inst{1}\orcidID{0000-1111-2222-3333} \and
Javier Cladellas \inst{1}\orcidID{} \and 
Abdoulaye Diallo \inst{1}\orcidID{} \and
Maryam Maslek \inst{1}\orcidID{} \and
Philippe Pinçon \inst{1}\orcidID{} \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\ 
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\authorrunning{V. Chabannes and C. Prud'homme}

@@

\begin{abstract}
The building sector in the European Union significantly impacts energy consumption and greenhouse gas emissions. The EU's Horizon 2050 initiative sets ambitious goals to reduce these impacts through enhanced building renovation rates. The HiDALGO2 project supports this initiative by developing high-performance computing solutions, specifically through the Urban Building pilot application, which utilizes advanced CI/CD methodologies to streamline simulation and deployment across various computational platforms.
\keywords{HPC, Urban building, City Energy Simulation.}

@@

\section{Introduction}
The building sector accounts for approximately 40\% of final energy consumption and 36\% of greenhouse gas emissions within the European Union. In response, the EU has established ambitious targets under the Horizon 2050 framework to double energy renovation rates over the next decade, highlighting the need for innovative solutions to drive these initiatives forward. The HiDALGO2 project, with its focus on high-performance computing and advanced simulations, is at the forefront of tackling this challenge, particularly through its Urban Building pilot application.

The Urban Building pilot in HiDALGO2 aims to leverage high-performance computing to enhance urban simulations for better energy management and air quality assessment. This section outlines the specific objectives and expected impacts of the project.

Advanced simulation tools are employed to predict energy consumption, thermal comfort, and indoor air quality across both the building and urban scales. These simulations support detailed analysis at the individual building level and extend to broader urban environments, influencing urban planning and policy-making.

Integrating building simulations with urban air pollution models enables the project to assess the environmental impact of building stocks comprehensively. This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness to environmental conditions.

@@

Feel++\cite{christophe_prudhomme_feelppfeelpp_2024}

\section{Current Urban Building Workflow}

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{images/kub-workflow.pdf}
    \caption{Current Urban Building Workflow}
    \label{fig:ub_workflow}
\end{figure}

The urban building workflow integrates various data sources and computational tools to effectively simulate and analyze urban building energy and its impact on urban environments. The process encompasses data acquisition, processing, simulation, and analysis, coupled with an integration into urban air pollution models.

\subsection{Data Handling and Simulation Process}
The workflow begins with the collection and preparation of GIS and weather data, transforming it into a format usable for simulations. This data is then partitioned for scalable processing, and converted into Modelica and Feel++ compatible formats through the UBEM Generator.

Using the Urban Building Energy Model (UBEM), this processed data is employed to simulate energy consumption and indoor environmental quality. The simulation focuses on radiative heat transfer, enhancing the accuracy of the energy models. It also computes view factors and shading masks, assessing how buildings affect each other’s exposure to natural light and heat, which influences the urban heat island effect and overall building energy needs.

The building simulation outputs are then fed into the Urban Air Pollution (UAP) simulator to evaluate the impact of building emissions on urban air quality. A feedback loop refines the building simulation scenarios based on intermediate outputs from the UAP simulator, ensuring that the models accurately reflect the complex interdependencies between urban building energy usage and urban air quality.

\subsection{Final Analysis and Urban Scale Energy Evaluation}
The final step involves the UBEM Simulator, which generates outputs summarizing the overall energy consumption and environmental impact of buildings at an urban scale. This comprehensive urban scale analysis merges data from both the building energy models and air quality models to provide a holistic view of urban environmental quality.

This streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting the broader objectives of our application to improve urban living conditions and environmental impact.

@@

\subsection{Geometry Reconstruction of the Urban Model}

The geometric reconstruction of urban environments within the HiDALGO2 project involves a sophisticated approach to creating multi-fidelity representations of buildings, terrain, vegetation, roads, and other urban elements. This section outlines the methodologies employed and the various levels of detail (LOD) used in the models.

The primary challenge lies in accurately representing the complex urban landscape to support various simulations. A tiled web map approach is adopted, which allows for distributed data management and adapts the Level of Definition (LOD) based on specific needs. However, this approach requires the careful integration of tiles to ensure seamless representation.

We describe our definition of Levels of Detail for Buildings
\begin{itemize}
    \item \textbf{LOD-0:} The simplest form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
    \item \textbf{LOD-1:} Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
    \item \textbf{LOD-2:} At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses. This includes detailed geometries for each entity of the building, often using complex surface models like B-REP, swept solids, or CSG techniques.
\end{itemize}

In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM.

\begin{figure}[htbp]
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod0.png}
  \caption{LOD-0: a building is represented by its bounding box}
  \label{fig:building-lod0}
\end{subfigure}%
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod1.png}
  \caption{LOD-1: a building is represented by its ground footprint elevated to its height}
  \label{fig:building-lod1}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod2.png}
  \caption{LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.}
  \label{fig:building-lod2}
\end{subfigure}%
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod2-zoom.png}
  \caption{LOD-2: A zoom on the LOD-@ building.}
  \label{fig:building-lod2-zoom}
\end{subfigure}
\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}
\end{figure}

Building meshes are generated from metadata fetched from web services like OpenStreetMap, which provides multi-polygons with holes, representing the complex urban fabric. For \textbf{LOD-0 and LOD-1}, buildings are modeled from 2D footprints extruded to form three-dimensional volumes. These volumes are then combined or subtracted to represent the district or the entire city, applying union operations on buildings that touch or intersect. In \textbf{LOD-2}, the focus shifts to creating conformal and watertight meshes that are suitable for detailed simulation tasks. These meshes are generated from Building Information Modeling (BIM) data in IFC format, enabling a detailed representation of each building component.

In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.

\subsubsection{Terrain Modeling}
The terrain modeling process utilizes elevation data extracted from raster images. The initial step involves creating a uniform mesh based on the size of the raster image. Following this, the elevation at each node is evaluated. Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible. Finally, each tile is glued together to ensure the continuity of the terrain mesh.

\subsubsection{Integration of Terrain and Building Meshes}
This process involves creating a conforming mesh that includes both the terrain and the buildings, ensuring that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect.

\subsubsection{Visual Representation}
Advanced rendering techniques are employed to visualize the multi-fidelity urban models, supporting both detailed analysis and general urban planning discussions. These visualizations are crucial for assessing the impact of urban changes and for stakeholder engagement.

This approach enhances the accuracy, utility, and scalability of urban models, making them vital for comprehensive urban analysis and planning in the HiDALGO2 project.

\begin{figure}[htbp]
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/city-strasbourg-lod-0.png}
  \caption{LOD-0}
  \label{fig:city-strasbourg-lod0}
\end{subfigure}%
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/city-strasbourg-lod-1.png}
  \caption{LOD-1}
  \label{fig:city-strasbourg-lod1}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/city-grenoble-terrain.png}
  \caption{LOD-1 terrain}
  \label{fig:city-grenoble-terrain}
\end{subfigure}
\caption{}
\label{fig:city-strasbourg}
\end{figure}

\subsubsection{Computational Tools for Building Meshes}

In the urban modeling process, particularly in the generation of building meshes, the Computational Geometry Algorithms Library (CGAL), plays a pivotal role. CGAL, \cite{the_cgal_project_cgal_2024} is renowned for its robust and efficient algorithms, which are crucial for handling complex geometric data and generating high-quality meshes from them.

\paragraph{Current Mesh Generation Strategy}
The current strategy for mesh generation employs multi-threading (MT) to handle various stages of the mesh construction process. Initially, the tiles to be used are determined based on the specified location, a task performed sequentially. Following this, GIS data, including buildings and elevation information, is downloaded in parallel. Next, polygons are repaired to ensure they are suitable for mesh generation, with this process executed in parallel using MT. The terrain mesh is then generated in parallel, employing CGAL's algorithms to ensure precision and efficiency. Union operations at tile junctions are performed to ensure continuity, a step that is currently sequential. Finally, building meshes are generated using a parallel MT approach, leveraging CGAL for its advanced mesh generation capabilities.

\paragraph{Advancing Towards Full Parallelism}
The next steps in enhancing the mesh generation process involve moving towards a fully parallel approach using both Multi-threading (MT) and Message Passing Interface (MPI). The goal is to scale the process up to handle entire cities or larger urban areas. This scale-up involves utilizing MPI to manage distributed computing resources effectively. To achieve this, partitions of tiles with overlapping areas are created to ensure complete and accurate building descriptions without the need for extensive MPI communication. Furthermore, each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.

\subsubsection{Partitioning Strategies Depending on Simulation Use Cases}
Different partitioning strategies are employed depending on the specific requirements of the simulation use cases. For simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient, known as Test Case 0. In Test Case 1, where buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings. For full interaction models, as in Test Case 2, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring that all elements are considered to minimize communication overhead. Looking towards scenarios with extreme partitioning needs, Test Case 3 employs a multigrid approach, defining coarse and fine meshes to efficiently manage computational resources. This multi-fidelity approach not only enhances the accuracy and applicability of urban models in simulations but also ensures scalability across different computational platforms, making it a cornerstone of urban analysis in the HiDALGO2 project.

The figure~\ref{fig:partitioning} illustrates the different strategies discussed previously and present a reconstruction of New York with 10km square reconstruction with hundreds of thousands of buildings which requires the large scale approach discussed but not yet implemented nor tested.
\begin{figure}[htbp]
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/city-strasbourg-lod0-parts.png}
  \caption{LOD-0}
  \label{fig:city-strasbourg-lod0-parts}
\end{subfigure}%
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/city-strasbourg-lod1-parts.png}
  \caption{LOD-1}
  \label{fig:city-strasbourg-lod1-parts}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/city-newyork-largescale.png}
  \caption{LOD-1 Large scale}
  \label{fig:city-ny-largescale}
\end{subfigure}
\caption{}
\label{fig:partitioning}
\end{figure}

\subsubsection{Conclusion on mesh construction}
Our strategy not only aims to improve the efficiency and scalability of the mesh generation process but also enhances the fidelity and accuracy of the urban models used in simulations.

@@

\subsubsection{Feel++ Toolchain}

@@

Key features of the Feel++ framework encompass an extensive range of numerical methods designed to address Partial Differential Equations (PDEs). These methods include continuous Galerkin (cG), discontinuous Galerkin (dG), hybrid discontinuous Galerkin (hdG), and reduced basis methods (rb/mor). A Domain Specific Language (DSL) for Galerkin methods significantly enhances the ease of implementing and experimenting with new numerical methods. The de Rham complex provides a comprehensive toolkit for constructing finite element spaces of arbitrary order, facilitating precise mathematical modeling. The framework's automatic differentiation and symbolic integration capabilities effectively bridge the gap between mathematical expressions and their computational implementation. Feel++ supports diverse applications from fluid dynamics and structural mechanics to heat transfer and electrostatics, demonstrating its flexibility and broad applicability. Furthermore, its integration with Specx for task-based parallel execution optimizes performance and scalability on modern computational architectures.

\paragraph{Simulation Tools and Applications}
Feel++ comes equipped with a variety of toolboxes tailored for specific application domains, offering pre-built scenarios for fluid dynamics, solid mechanics, and electromagnetism, among others. These toolboxes are designed to provide robust and efficient solutions, leveraging the capabilities of Feel++ to address complex multi-physics problems in real-world scenarios.

Documentation and further details can be accessed through Feel++ Toolboxes Documentation\footnote{\url{https://docs.feelpp.org/toolboxes/latest/}}.
This powerful toolchain is essential for the Urban Building pilot of the HiDALGO

>>>>

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage[]{subcaption}

\usepackage{url}
\usepackage{tikz}
\usepackage{xcolor}
\definecolor{darkred}{rgb}{0.6, 0, 0}
\definecolor{darkgreen}{rgb}{0, 0.5, 0}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,      % Enable colored links
    linkcolor=darkred,    % Color for internal links
    filecolor=darkgreen,  % Color for file links
    urlcolor=darkblue,    % Color for external URLs
    citecolor=darkmagenta % Color for citations
}

\begin{document}
\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{}
\author{Luca Berti (formerly)\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and 
Abdoulaye Diallo \inst{1}\ \and
Maryam Maslek Elayam \inst{1} \and
Philippe Pinçon \inst{1} \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\ 
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\authorrunning{V. Chabannes et al.}

@@

\begin{abstract}
The building sector in the European Union significantly impacts energy consumption and greenhouse gas emissions. The EU's Horizon 2050 initiative sets ambitious goals to reduce these impacts through enhanced building renovation rates. The CoE HiDALGO2 supports this initiative by developing high-performance computing solutions, specifically through the Urban Building pilot application, which utilizes advanced CI/CD methodologies to streamline simulation and deployment across various computational platforms, such as the EuroHPC JU supercomputers. The present work provides an overview of the Ktirio Urban Building framework (KUB), starting with an overview of the workflow and a description of some of the main ingredients of the software stack and discusses some current results performed on EuroHPC JU supercomputers using an innovative CI/CD pipeline.

\keywords{HPC, HPCOps, Urban building, City Energy Simulation.}

@@

\section{Introduction}
The building sector accounts for approximately 40\% of final energy consumption and 36\% of greenhouse gas emissions within the European Union~\cite{european_commision_energy_2020}. In response, the EU has established ambitious targets under the Horizon 2050 framework to double energy renovation rates over the next decade~\cite{european_commision_stakeholder_2021}, highlighting the need for innovative solutions to drive these initiatives forward. The Centre of Excellence (CoE) HiDALGO2 project, focusing on high-performance computing and advanced simulations, is at the forefront of tackling this challenge, mainly through its Urban Building pilot application.

The Ktirio Urban Building (KUB) pilot in CoE HiDALGO2 aims to leverage high-performance computing to enhance city energy simulation for better energy management and air quality assessment. Advanced simulation tools predict energy consumption, thermal comfort, and indoor air quality across both the building and urban scales. These simulations support detailed individual building-level analysis and extend to broader urban environments, influencing urban planning and policy-making.

Building on the foundations of the Feel++ framework, our project introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers. This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying these simulations at scale. Integrating EuroHPC JU infrastructures represents a significant advancement in making high-performance computing resources accessible for urban simulation studies.

Thanks to synergies with another CoE HiDALGO2 pilot, the KUB project is set to integrate building simulations with urban air pollution (UAP) models to comprehensively assess the environmental impact of building stocks soon. This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness to environmental conditions.

@@

The paper is organized as follows: Section 2 discusses KUB's current workflow, Section 3 provides an overview of some modeling and simulation components, and finally, Section 4 delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.

%Feel++\cite{christophe_prudhomme_feelppfeelpp_2024}

\section{Ktirio Urban Building Workflow}

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{images/kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments. The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with urban air pollution (UAP) models.

\subsection{Data Handling and Simulation Process}
The workflow begins with collecting and preparing GIS and weather data, transforming it into a format usable for simulations. This data is then partitioned for scalable processing and converted into Modelica and Feel++\cite{christophe_prudhomme_feelppfeelpp_2024} compatible formats through the UBEM Generator.

This processed data is employed to simulate energy consumption and indoor environmental quality using the Urban Building Energy Model (UBEM). The simulation focuses on radiative heat transfer, enhancing the accuracy of the energy models. It also computes view factors and shading masks, assessing how buildings affect each other's exposure to natural light and heat, influencing the urban heat island effect and overall building energy needs.

The building simulation outputs are then optionally fed into the urban air pollution (UAP) simulator to evaluate the impact of building emissions on urban air quality. A feedback loop refines the building simulation scenarios based on intermediate outputs from the UAP simulator, ensuring that the models accurately reflect the complex interdependencies between urban building energy usage and urban air quality.

\subsection{Final Analysis and Urban Scale Energy Evaluation}
The final step involves the UBEM Simulator, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale. This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.

This streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting our application's broader objectives of improving urban living conditions and environmental impact.

@@

\subsection{Geometry Reconstruction of the KUB Urban Model}

The geometric reconstruction of urban environments within KUB involves a sophisticated approach to creating multi-fidelity representations of buildings, terrain, vegetation, roads, and other urban elements. This section outlines the methodologies employed and the various levels of detail (LOD) used in the models.

The primary challenge lies in accurately representing the complex urban landscape to support various simulations. A tiled web map approach is adopted, which allows for distributed data management and adapts the Level of Detail (LOD) based on specific needs. However, this approach requires carefully integrating tiles to ensure seamless representation.

We describe our definition of Levels of Detail for Buildings such as:
\begin{itemize}
    \item \textbf{LOD-0:} The most straightforward form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
    \item \textbf{LOD-1:} Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
    \item \textbf{LOD-2:} At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses. This includes detailed geometries for each building entity, often using complex surface models like B-REP, swept solids, or CSG techniques.
\end{itemize}

\begin{wrapfigure}{R}{0.6\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.48\linewidth]{images/buildings-lod0.png}
  \label{fig:building-lod0}
}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.48\linewidth]{images/buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
  \includegraphics[width=0.48\linewidth]{images/buildings-lod2.png}
  \label{fig:building-lod2}
}
%\hfill
\subfloat[LOD-2: A zoom on the LOD-2 building.]{%
  \includegraphics[width=0.48\linewidth]{images/buildings-lod2-zoom.png}
  \label{fig:building-lod2-zoom}
}

\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}
\end{wrapfigure}
In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.

\subsubsection{Building Modeling}
Building meshes are generated from metadata fetched from web services like OpenStreetMap~\cite{openstreetmap_contributors_planet_2017}, which provides multi-polygons with holes representing the complex urban fabric. For \textbf{LOD-0 and LOD-1}, buildings are modeled from 2D footprints extruded to form three-dimensional volumes. These volumes are then combined or subtracted to represent the district or the entire city, applying union operations on buildings that touch or intersect. In \textbf{LOD-2}, the focus shifts to creating conformal and watertight meshes suitable for detailed simulation tasks. These meshes are generated from Building Information Modeling (BIM) data in IFC format, enabling a detailed representation of each building component.

\subsubsection{Terrain Modeling}
The terrain modeling process utilizes elevation data extracted from raster images. The initial step involves creating a uniform mesh based on the size of the raster image. Following this, the elevation at each node is evaluated.
However, this method provides a very refined mesh, even when the terrain is flat. For this reason, we plan to apply the following procedure:
\begin{itemize}
    \item Compute an arbitrary number of isolines for elevation,
    \item Build a new terrain mesh conform with the isolines nodes and adapt to terrain elevation gradient.
\end{itemize}
%Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible. Finally, each tile is glued together to ensure the continuity of the terrain mesh.

\subsubsection{Vegetation Modeling}
Including vegetation (trees) in this geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas has a significant impact. 
We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:
\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

\subsubsection{Integration of all urban geometric components}
This process involves creating a conforming mesh that includes both components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain. 
And \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

\subsubsection{Visual Representation}
Advanced rendering techniques visualize the multi-fidelity urban models, supporting detailed analysis and general urban planning discussions. These visualizations are crucial for assessing the impact of urban changes and for stakeholder engagement.

This approach enhances urban models' accuracy, utility, and scalability, making them vital for comprehensive urban analysis and planning in the HiDALGO2 project.

\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
  \includegraphics[width=0.4\textwidth]{images/city-strasbourg-lod-0.png}
}
\hfill % Ensures that the images are placed side by side
\subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
  \includegraphics[width=0.4\textwidth]{images/city-strasbourg-lod-1.png}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
  \includegraphics[width=0.4\textwidth]{images/city-grenoble-terrain.png}
}

\caption{Various representations of cities and terrain. Representation of Strasbourg center with LOD-0 in the top left panel and LOD-1 in the top right. LOD-1 city (Grenoble, France) representation with terrain elevation.}
\label{fig:city-strasbourg}
\end{wrapfigure}

\subsubsection{Computational Tools for Meshes Generation}

In the urban modeling process, particularly in generating building meshes, the Computational Geometry Algorithms Library (CGAL) plays a pivotal role. CGAL, \cite{the_cgal_project_cgal_2024} is renowned for its robust and efficient algorithms, which are crucial for handling complex geometric data and generating high-quality meshes. This library is currently used for the following operations: boolean operation of polygon, multi-polygon repairs, mesh generation, mesh intersection, mesh adaptation, and building roof skeleton.

All the features described above are not yet operational in our framework. We can reconstruct a geometric model of an urban area whose location is arbitrary so that the user can select an area anywhere in the world. The final mesh comprises all buildings LOD-0 or LOD-1 and the terrain with elevation. The integration of all the urban components is currently being investigated. This part requires fairly costly algorithms (mesh intersection), for which it will be necessary to form groups intelligently to reduce the computational cost.

\paragraph{Current Mesh Generation Strategy}
The current strategy for mesh generation employs multi-threading (MT) to handle various stages of the mesh construction process. Initially, the tiles used are determined based on the specified location, a task performed sequentially. Following this, GIS data, including buildings and elevation information, is downloaded in parallel. Next, polygons are repaired to ensure they are suitable for mesh generation, with this process executed in parallel using MT. The terrain mesh is then generated in parallel, employing CGAL's algorithms to ensure precision and efficiency. Union operations at tile junctions are performed to ensure continuity, a step that is currently sequential. Finally, building meshes are generated using a parallel MT approach, leveraging CGAL for its advanced mesh generation capabilities.

\paragraph{Advancing Towards Full Parallelism}
The following steps in enhancing the mesh generation process involve moving towards a fully parallel approach using both Multi-threading (MT) and Message Passing Interface (MPI). The goal is to scale the process to handle entire cities or larger urban areas. This scale-up involves utilizing MPI to manage distributed computing resources effectively. To achieve this, partitions of tiles with overlapping regions are created to ensure complete and accurate building descriptions without requiring extensive MPI communications. Furthermore, each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.

\subsubsection{Partitioning Strategies Depending on Simulation Use Cases}
Data partitioning is a crucial stage in the deployment of the supercomputer simulator. We need to partition the geometry of the city in such a way as to distribute the simulation computation correctly.
Different partitioning strategies are considered depending on the specific requirements of the simulation use cases :
\begin{itemize}
\item Case 0: simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient
\item Case 1: buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings. The build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately.
\item  Case 2: for full interaction models, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead.
\item Case 3: Regarding scenarios with extreme partitioning needs, Test Case 3 employs a multi-grid approach, defining coarse and fine meshes to manage computational resources efficiently. This multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
\end{itemize}

The current version of our simulation framework has implemented case 0 and case 1. Cases 2 and 3 require a full conformal mesh, which is not yet available. Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
  \includegraphics[width=0.48\linewidth]{images/city-strasbourg-lod0-parts.png}
}
%\hfill % Ensures that the images are placed side by side
\subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
  \includegraphics[width=0.48\linewidth]{images/city-strasbourg-lod1-parts.png}
}
%\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
%  \includegraphics[width=0.4\textwidth]{images/city-newyork-largescale.png}
%}
\caption{Mesh partitioning illustrations}
\label{fig:partitioning}
\end{wrapfigure}

The figure~\ref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in figure \ref{fig:city-ny-largescale}. This geometric model has an area of 400 $km^2$ (20 km square side of 20 km) and has generated around 450000 buildings. This example requires the large-scale approach discussed but not yet implemented or tested.

\begin{figure}[htbp]
\centering
\subfloat[View on whole 3D mesh\label{fig:city-ny-largescale-whole}]{%
  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-whole.png}
}
\hfill
\subfloat[Zoom on Manhattan buildings\label{fig:city-ny-largescale-zoomB}]{%
  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomB.png}
}\\
\subfloat[Focus on Manhattan\label{fig:city-ny-largescale-zoomZ}]{%
  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomA.png}
}
\hfill
\subfloat[Central Park\label{fig:city-ny-largescale-zoomC}]{%
  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomC.png}
}
\caption{$20 \times 20 \mathrm{km}^2\ $ geometric reconstruction of New York City (LOD-1)}
\label{fig:city-ny-largescale}
\end{figure}

\subsubsection{Conclusion on mesh construction}
Our strategy aims to improve the efficiency and scalability of the mesh generation process and enhance the fidelity and accuracy of the urban models used in simulations.

@@

\subsubsection{KUB is based on the Feel++ toolchain}

@@

Key features of the Feel++ framework encompass an extensive range of numerical methods designed to address Partial Differential Equations (PDEs), see~\cite{christophe_prudhomme_feelppfeelpp_2024}. These methods include continuous Galerkin (cG), discontinuous Galerkin (dG), hybrid discontinuous Galerkin (hdG), and reduced basis methods (rb/mor). A Domain Specific Language (DSL) for Galerkin methods significantly enhances the ease of implementing and experimenting with new numerical methods. The de Rham complex provides a comprehensive toolkit for constructing finite element spaces of arbitrary order, facilitating precise mathematical modeling. The framework's automatic differentiation and symbolic integration capabilities effectively bridge the gap between mathematical expressions and their computational implementation. Feel++ supports diverse applications, from fluid dynamics and structural mechanics to heat transfer and electrostatics, demonstrating its flexibility and broad applicability. Furthermore, its integration with Specx for task-based parallel execution optimizes performance and scalability on modern computational architectures.

%\paragraph{Simulation Tools and Applications}
%Feel++ comes equipped with various toolboxes tailored for specific application domains, offering pre-built scenarios for fluid dynamics, solid mechanics, and electromagnetism, among others. These toolboxes are designed to provide robust and efficient solutions, leveraging the capabilities of Feel++ to address complex multi-physics problems in real-world scenarios.

Documentation and further details can be accessed through Feel++ Toolboxes Documentation\footnote{\url{https://docs.feelpp.org/toolboxes/latest/}}.
This powerful toolchain is essential for KUB.
